---
title: "Data Wrangling"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Part Α 

**The following data were used :**

```{r}
library(tidyverse)

data <- tribble(
  ~happy, ~uptempo, ~blues, ~jazz, ~gospel,
  "yes", "yes", 10, 5, 20,
  "no", "no", NA, 12, 15,
  "yes", "no", 7, 6, 4,
  "no", "yes", 3, NA, NA
)

```


```{r}

data_tidy1 <- data %>% 
  gather(key = "genre", value = "count", c(-happy, -uptempo))
data_tidy1

```


```{r}

data_tidy2 <- data_tidy1 %>% 
  filter(!is.na(count))
data_tidy2

```



```{r}
data_tidy3 <- data_tidy2 %>%
  select(-uptempo) %>%  
  mutate(happy = ifelse(happy=="yes", TRUE,FALSE)) %>%
  mutate(genre = ifelse(genre=="jazz", TRUE,FALSE)) %>%
  rename(jazz = genre) %>% 
  group_by(happy, jazz) %>% 
  summarise(total = sum(count[happy == TRUE & jazz == TRUE],
                        count[happy == TRUE & jazz== FALSE],
                        count[happy == FALSE & jazz == FALSE],
                        count[happy == FALSE & jazz == TRUE])) %>%
  relocate(jazz) %>%
  arrange(jazz)
data_tidy3
```



```{r}

data_tidy2_d <- subset(data_tidy2, genre == "jazz" & happy == "no", select=c(count))
data_tidy2_d
data_tidy3_d <- subset(data_tidy3, jazz == TRUE & happy == FALSE, select=c(total))
data_tidy3_d

```

## Part Β

**The following data were used :**

**Load the data...**

```{r}
library(tidyverse)
who <- tidyr::who
view(who)
```


```{r}
dict_url <- "https://extranet.who.int/tme/generateCSV.asp?ds=dictionary"
if (!file.exists("dict.csv")) download.file(dict_url, "dict.csv")
dict <- read_csv('dict.csv')
view(dict)
labels <- data.frame(name = colnames(who))
view(labels)
explanations <- semi_join(dict, labels, by=c("variable_name" = "name"))
view(explanations)
```

**Convert the table to have the following format: who(country, iso2, iso3, year, notification, cases). Ignore NA values.**

```{r}
who <- who %>%
  gather(key = "notification", value = "cases", c(new_sp_m014:newrel_f65)) %>%
  filter(!is.na(cases)) 
who
```

**Replace all occurrences of the string "newrel" in the notification column with the string "new_rel".**

```{r}
who <- who %>%
  mutate(across('notification', str_replace, 'newrel', 'new_rel')) 
who
```

**Split the contents of the notification column into the new, type, sex, age columns.**

```{r}
who <- who %>%
  separate(notification, into = c("new", "type", "sex"), sep = "_") %>%
  separate(sex, into = c("sex", "age"), sep ="(?<=[A-Za-z])(?=[0-9])") 
who
```

**Remove the columns new, iso2, iso3.**

```{r}
who <- who %>%
  select(-new, -iso2, -iso3)
who
```

**Calculate the total number of TB cases for each country.**

```{r}
who5 <- who %>%
  select(-year, -type, -sex, -age) %>% 
  group_by(country) %>% 
  summarise(count = sum(cases))
who5
```

**Find for each year the country with the highest number of smear positive pulmonary TB cases (sp).**

```{r}
who6 <- who %>%
  select(year,country,cases) %>% 
  group_by(year) %>%
  slice(which.max(cases))
who6
```

**For Greece only, provide a table with only 3 columns: year, f, and m, where the values for columns m and f are the total TB cases for women and men respectively. The table should be sorted in descending order by f+m, i.e. the total number of TB cases.**

```{r}
who7 <- who %>%
  filter(country == "Greece")%>% 
  select(year,sex,cases) %>%
  pivot_wider(names_from = sex, values_from = cases, values_fn = sum) %>%
  relocate(m, .after = f) %>%
  arrange(desc(f+m)) 
who7
```

