---
title: "Data Visualization"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Part 1**

**Load the data**

```{r}
library(tidyverse)
library(ggplot2)

queen <- read_csv("queen.csv")
head(queen)
```

**Create a bar chart that shows the number of tracks in each album.**

```{r}
ggplot(data = queen) +
  geom_bar(mapping = aes(x = album_name), fill = "lightblue") +
  coord_flip()
```

**Plot a histogram (with 15 bins) showing the distribution of the tempo values of the tracks, using the aesthetic fill to show the mode distribution of the tracks in each bin.**

```{r}
ggplot(queen, aes(x = tempo, fill = mode)) + 
  geom_histogram(bins = 15)
```

**Display the tempo box plots by album.**

```{r}
ggplot(queen, aes(x = album_name, y = tempo)) + 
  geom_boxplot() + xlab("")
```

**Using the aesthetic size for tempo, create a faceted scatter plot for each album in terms of danceability and energy.**

```{r}
ggplot(queen, aes(danceability, energy, size = tempo)) +  
  geom_point() +
  facet_wrap(~album_name)
```

**Scatterplot of the relationship between danceability and track popularity.**

```{r}
ggplot(queen, aes(danceability, track_popularity)) +
  geom_point() +
  ggtitle("Relationship between danceability and popularity")
```

**Chart showing the popularity of each album in ascending order.**

```{r}
ggplot(queen, aes(x = album_popularity, y = reorder(album_name,album_popularity))) +
  geom_point(color = "blue") +
  ylab("Albumns from 1973 - 1991") +
  xlab("Popularity of Queen's albums\n")
```

**Part 2**

**Load the data**
```{r}
mc <- read_csv("mcdonalds.csv")
head(mc)
```

**Calculate the values of the BIG MAC in US dollars.**

```{r}
mc<- mc%>%
  mutate(priceDollars=local_price / dollar_ex)
mc
```

**Scatterplot of the GDP of the countries and the value of the BIG MAC in US dollars.**

```{r}
ggplot(data = mc, mapping = aes(x = GDP_dollar, y = priceDollars)) +
  geom_point()
```